---
title: "<code>revealjs</code> <i class=\"fas fa-heart\"></i> <code>rmarkdown</code>"
subtitle: "This is a revealjs presentation"
author: "Created by <a href='' target='_blank'>My Name</a>"
date: "March 22, 2005<div style='margin-top:50px;'><a href='' target='_blank'><i style='margin-right:70px;' class='fab fa-linkedin fa-3x'></i></a><a href='https://github.com/schalkdaniel/revealjsRmd' target='_blank'><i style='margin-right:70px;' class='fab fa-github fa-3x'></i></a><a href='' target='_blank'><i class='fab fa-twitter fa-3x'></i></a></div>"
output:
  revealjs::revealjs_presentation:
    css: myreveal.css
    transition: slide
    includes:
      in_header: header.html
      after_body: after.html
    self_contained: false
    reveal_options:
      controls: true
      controlsTutorial: true
      center: true
      slideNumber: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

# Ordinary Markdown

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure, fig.align="center", out.width="50%"}
plot(pressure)
```

# That's it, thanks for your attention!

## Credits

- [**revealjs**](https://revealjs.com/)
- [**Font-Awesome:**](https://www.google.com)
- [**rmarkdown**](https://rmarkdown.rstudio.com/)
- [**revealjs (R Package)**](https://cran.r-project.org/web/packages/revealjs/index.html)
- [**Google Fonts**](https://fonts.google.com/)


